RNA-seq from 4 cell populations

### 2020-08-21 deconvolution/fans4/molec_profiling.Rmd
Initial commit

```{r mvIC}
colnames(info) = gsub(' ', '_', colnames(info))
colnames(info) = gsub(':', '', colnames(info))
colnames(info) = gsub('\\(', '', colnames(info))
colnames(info) = gsub(')', '', colnames(info))
colnames(info) = gsub('/', '', colnames(info))
colnames(info) = gsub('-', '_', colnames(info))
colnames(info) = gsub(',', '', colnames(info))

>>>>

```{r mvIC, eval=FALSE}
colnames(info) = gsub(' ', '_', colnames(info))
colnames(info) = gsub(':', '', colnames(info))
colnames(info) = gsub('\\(', '', colnames(info))
colnames(info) = gsub(')', '', colnames(info))
colnames(info) = gsub('/', '', colnames(info))
colnames(info) = gsub('-', '_', colnames(info))
colnames(info) = gsub(',', '', colnames(info))
